Democracy, Public Support, and Measurement Uncertainty

### 2021-07-21 paper/dcpo_demsupport.Rmd
adjust citation

Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey_policy_2018, p.254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p. 18; @Gandhi2020, p. 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp. 791-792; @caughey_policy_2018, p. 254].

>>>>

Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey2018, p.254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p. 18; @Gandhi2020, p. 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp. 791-792; @caughey2018, p. 254].
